Spatial Reasoning and Statistical Graphics

### 2014-11-17 Paper/Draft1/TestingVisualAptitude.Rnw
Remove newtext since it's been there a while

\newtext{One of the most useful features of the lineup protocol is that it allows researchers to conclusively determine which graphics show certain features more conclusively (providing an experimental protocol for comparing graphics based on the accuracy of user conclusions). In addition, lineups provide researchers with a rigorous framework for determining whether a specific graph shows a real, statistically significant effect by comparing a target plot with plots formed using permutations of the same data, providing a randomization test protocol for graphics. As a result, lineups are a useful and innovative tool for evaluating charts; on an individual level, they can also be used to evaluate a specific participant's perceptual reasoning ability in the context of statistical graphics.}

>>>>

One of the most useful features of the lineup protocol is that it allows researchers to conclusively determine which graphics show certain features more conclusively (providing an experimental protocol for comparing graphics based on the accuracy of user conclusions). In addition, lineups provide researchers with a rigorous framework for determining whether a specific graph shows a real, statistically significant effect by comparing a target plot with plots formed using permutations of the same data, providing a randomization test protocol for graphics. As a result, lineups are a useful and innovative tool for evaluating charts; on an individual level, they can also be used to evaluate a specific participant's perceptual reasoning ability in the context of statistical graphics.
